Forecasting the black Sigatoka development rate: A comparison of machine learning techniques

### 2015-11-24 Paper Sigatoka - 2015.tex
Lunes 23 noche, cambios en tema de sigatoka

According to studies by the National Banana Corporation of Costa Rica
(Corbana) made in 2013, considering on average between 53 thru 57
cycles of fungicide applications per farm, the cost per hectare per
year ranged between \$1800 USD and \$1900 USD. This represents
about 0.76 cents of the price of a box of 18.14 kilograms. Overall,
this represents 10\% to 12\% of the total production cost
\citet{Bresciani2015}.
\marginnote{Hay que completar la cita de Brescani, o cambiarla}

@@

This system measures the disease development state to determine when to
apply fungicides \citep{MarinVargas1995}.  This system is based on two
components: a climate component, which is given by the Piche
evaporation and a biological component, given by the stage of progress
or the rate of disease development. Originally, this system was
designed to work with young plants. One selected plant must exhibit a
normal growth and be in a place that enforces a healthy
development. The plant must start with 5 to 6 true leaves. The
assessments are made at fixed intervals of seven days as long as
possible, on the same plant. The first observations should consider
the leaf emission, also the level of infection on the leaves should be
evaluated considering the stages of development
\citep{MarinVargas1995}.
\marginnote{Tendra sentido ampiar esta parte?}

@@

\bibitem[Brescani, 2015]{Bresciani2015} Brescani, XXXXX.

@@

@@

\bibitem[Pedregosa et al., 2013] {scikitlearn2011} Pedregosa, F. and Varoquaux, G. and Gramfort, A. and Michel, V. and Thirion, B. and Grisel, O. and Blondel, M. and Prettenhofer, P. and Weiss, R. and Dubourg, V. and Vanderplas, J. and Passos, A. and Cournapeau, D. and Brucher, M. and Perrot, M. and Duchesnay, E. (2011) Scikit-learn: Machine Learning in {P}ython. Journal of Machine Learning Research, vol. 12, 2825--2830.

@@

\bibitem[Huang et al., 2010] {Huang2010}  Huang, Y., Lan, Y., Thomson, S., Fang, A., Hoffmann, W., Lacey, R. (2010). Development of soft computing and applications in agricultural and biological engineering. Computers and Electronics in Agriculture,(71(2)), 107–127. doi:10.1016/j.compag.

>>>>

In Costa Rica for the control of black Sigatoka is necessary the application of chemical fungicides. Depending of the zone of production and the weather conditions 45 – 55 cycles/year of fungicides is needed to keep this disease under control and to produce fruit with quality for exportation. This represent a cost per hectare per year ranged between \$1600 USD and \$2000 USD, about 0,64 - 0.80 cents of the cost of production of a box of 18.14 kilograms. Overall, this represents 10\% to 12\% of the total production cost.

@@

The early warning system for black Sigatoka is an adaptation of the yellow Sigatoka warning system developed by Ganry and Meyer and modified by Ganry and Laville to use for controlling yellow Sigatoka in Cameroon. Ternesien and Fouré  later improved Ganry and Laville's system. The latter system is based on weekly observations of disease symtoms on young leaves of the plant, according to Fouré's symptom (stages) descriptions. Arbitrary coefficientes, based on incidence and severity of disease development, are used to calculate two variables: gross sum and state of evolution. Gross sum is based on the stage present and an arbitrary coefficient, which increases with the advance of the symptoms and the juvenility of the leaf. The state of evolution is calculated using the gross sum and the foliar emission period. Although threshold levels were initially suggested as a guide to spray timing, the fluctuation of these two variables was found to better define appropiate times to spray \citep{Marinetal2003}.

@@

@@

\bibitem[Marin et al., 2003]{Marinetal2003} Marin, D., Romero, R., Guzman, M, Sutton, T. 2003. Black Sigatoka: An increasing threat to banana cultivation. Plant Disease, 87(3), 208-222.

@@

\bibitem[Pedregosa et al., 2013] {scikitlearn2011} Pedregosa, F. and Varoquaux, G. and Gramfort, A. and Michel, V. and Thirion, B. and Grisel, O. and Blondel, M. and Prettenhofer, P. and Weiss, R. and Dubourg, V. and Vanderplas, J. and Passos, A. and Cournapeau, D. and Brucher, M. and Perrot, M. and Duchesnay, E. (2011) Scikit-learn: Machine Learning in Python. Journal of Machine Learning Research, vol. 12, 2825--2830.

@@
